Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-19 ms.tex
more description of Kepler analysis.

\section{Kepler Re-analysis}
We examine the 17 total quarters of Kepler data.
There is not detectable secondary eclipse at $\lesssim 50$ ppm, seen in Figure \ref{fig:secEclipse}. 
The constraint is even tighter assuming a circular orbit.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/kepler/secondary_eclipse.pdf}
\caption{Secondary eclipse found by averaging the light curve from 17 quarters of Kepler data.}\label{fig:secEclipse}
\end{centering}
\end{figure*}

We create a cleaned Kepler long-cadence data set by interpolating all time series data onto a fixed phase grid with a spacing of 30 minutes.

>>>>

\section{Kepler Re-analysis}
We examine the 17 total quarters of Kepler data for three purposes:
\begin{enumerate}
	\item To understand the statistics of the transits and put our 2013-2016 observations in context. Mainly, how likely/unlikely were the weak transits observed in 2013-2014?
	\item To measure the radius of the planet or put an upper limit on its radius by examining any possible transit beneath the dust signal
	\item Identify any new patterns or observations from the Kepler data that might occur along the way
\end{enumerate}

We downloaded all 17 quarters of Kepler Long-Cadence data from the MAST archive beginning on 2009-05-13 and ending on 2013-04-08 for a total of 1425 days or 2181.5 orbits.
The Kepler data were examined for one transit or secondary eclipse at a time with a window of $\pm$0.28 in orbital phase.
A quadratic baseline is fit to all the points before a phase of 0.12 and after a phase of 0.15 with thin the $\pm$ 0.28 window.
All points are divided by this baseline to produce a normalized flux transit or eclipse profile.
The secondary eclipses are used to quantify the noise in the transit depths.

We confirm the result of \citet{vanWerkhoven2014} that no secondary eclipse is detected a at $\lesssim 50$ ppm, seen in Figure \ref{fig:secEclipse}. 
The constraint is even tighter assuming a circular orbit.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/kepler/secondary_eclipse.pdf}
\caption{No secondary eclipse ( $\lesssim$ 50 ppm) is detected from a phase range of -0.25 to 0.75, even with 17 quarters (4 years) of Kepler Long Cadence data.
Here the data are binned to orbital phases of 0.1 or 1.5 minutes and errors calculated from the standard error in the mean of the data.
}\label{fig:secEclipse}
\end{centering}
\end{figure*}

In order to perform some analysis techniques on the data and to study the transit depth behavior, we first create a uniform cleaned two dimensional array of the time series.
We interpolated the Kepler long-cadence data set onto a fixed phase grid with a spacing of 30 minutes and put together all the time series that have no gaps into this two dimensional grid.
This cleaned Kepler long-cadence array is shown in Figure \ref{fig:kepPCA}.
